Response to reviewers

### 2025-05-26 src/docs_paper-jtb/revisions.Rmd
Figure update text

We agree that there are too many colours here for this figure to be clear.
Thank you for the suggestion to split the plot into multiple panels.
We have done this, choosing to group the parameters by the component of the model they are most associated with.
(Remains to do this!)

>>>>

We agree that there are too many colours here for this figure to be clear, and that the suggestion to split the figure across panels is a good one.
To do so, we have grouped the parameters by the model component (e.g. HIV prevalence), and used colour to represent the type of parameter (e.g. intecept).

```{r}
knitr::include_graphics("depends/ks-summary.png")
```
